Pre-Trained Denoising Autoencoders Long Short-Term Memory Networks as probabilistic Models for Estimation of Distribution Genetic Programming

### 2023-01-11 paper.Rmd
autogit

![Population Diversity over 30 Generations - Airfoil](./img/airfoil_FullRun_30gens/mean_popDiversity_byGens.png)
Since @dae-gp_2022_symreg shows, that DAE-GP finds higher quality that are also smaller in size than those found by average GP for a given number of 10.000 fitness evaluations, I also studied the differences in average solution size between pre-trained and regular DAE-GP.

![Average Solution Size over 30 Generations - Airfoil](./img/airfoil_FullRun_30gens/mean_Size_byGens.png)

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c"
 #caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=FALSE) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

>>>>

![Population Diversity over 30 Generations - Airfoil](./img/airfoil_2hl_maxIndSize_fullRun_30gens/mean_popDiversity_byGens.png)
Since @dae-gp_2022_symreg shows, that DAE-GP finds higher quality that are also smaller in size than those found by average GP for a given number of 10.000 fitness evaluations, I also studied the differences in average solution size between pre-trained and regular DAE-GP.

![Average Solution Size over 30 Generations - Airfoil](./img/airfoil_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png)

@@

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "l"
 #caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=FALSE) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

### 2023-01-11 slides.Rmd
Wed Jan 11 17:00:11 CET 2023: update-remote.sh
autogit

![Airfoil - Erste Generation Median Trainingsfehler - Variable Anzahl Hidden Layer](./img/airfoil_firstGen/airfoil_firstGen_median_training_error_by_layers.png){height=85%}

@@

![Airfoil - Erste Generation Median Trainingsfehler - Variable Anzahl Hidden Neurons](./img/airfoil_firstGen/airfoil_firstGen_median_training_error_by_neurons.png){height=85%}

@@

![Energy (Cooling) Datensatz - Fitness über Generationen](~/masterThesis/master_thesis/img/energyCooling_2hl_FullRun_30gens/mean_median_fitness_byGens.png)

@@

\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} \\
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png}
\end{tabular}

>>>>

![Airfoil - Erste Generation Median Trainingsfehler - Variable Anzahl Hidden Layer](./img/airfoil_firstGen/airfoil_firstGen_median_training_error_by_layers_6plots.png){height=85%}

@@

![Airfoil - Erste Generation Median Trainingsfehler - Variable Anzahl Hidden Neurons](./img/airfoil_firstGen/airfoil_firstGen_median_training_error_by_neurons_6plots.png){height=85%}

@@

![Energy (Cooling) Datensatz - Fitness über Generationen](~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/mean_median_fitness_byGens.png)

@@

\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} \\
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/concrete_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png}
\end{tabular}
